\mytitle

### 2012-03-23 papers/SAS2012/implicitization.tex
...

Table \ref{tab:time} \MM{TODO} gives the execution time of the different analysis
techniques. It is interesting to see that 
\emph{Path-focusing} technique is sometimes faster than the classical algorithm.
This seems due to the fact that this technique avoids many convex hulls, which
is costly, and also computes the image of an abstract value by an entire path
instead of many single transitions.
The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.

>>>>

Table \ref{tab:time} \MM{TODO} gives the execution time of the different analysis
techniques. It is interesting to see that 
\emph{Path-focusing} technique is sometimes faster than the classical algorithm.
This seems due to the fact that this technique avoids many convex hulls, which
is costly, and also computes the image of an abstract value by an entire path
instead of many single transitions, thus leading to a large parallel assignment.
The techniques we introduce in this article are slower, but speed is still on the same order of magnitude as the older ones.
